Graphical Tests for Power Comparison of Competing Designs

### 2012-03-31 intro.tex
smallish change
removed repeat power definition, made notation consistent

\begin{quote}
Let $n$ be the number of independent observers and $x_i$ the number of observers who picked plot $i$, $i \in \{1, ..., m\}$, from the lineup. Then $(x_1, x_2, ..., x_m)$ follows a multinomial distribution Mult$_{\pi_1, \pi_2, ..., \pi_m}(x_1, x_2, ..., x_m)$ with $\sum_i \pi_i = 1$, where $\pi_i$ is the probability that plot $i$ is picked by an observer, which we can estimate as $\widehat{\pi_i} = x_i/n$. 
\end{quote}

@@

\section{Comparison of Designs}\label{designs}
We are going to make use of the signal strength gained from multiple viewings of a lineup in order to evaluate competing designs as follows:
\begin{enumerate}
\item{{\bf Create Lineup Data:} create data for a lineup of size $m$ by  creating  $m-1$ permutations of $y$ or, in the case of a simulation study, drawing $m-1$ samples of size $n$ (the number of rows in the data) from the null distribution. Add the original data to the lineup data randomly between 1 and $m$. }
\item{{\bf Create lineups from competing designs:} using the same data, render lineups of all competing designs. }
\item{{\bf Evaluate Lineups:} by presenting the lineups to independent observers. Assess both signal strength and time needed by individuals to come to a decision. Note that each observer should only be exposed to each lineup data once.}
\item{{\bf Evaluate Competing Designs:} differences in signal strength or time to decision are due to differences in the design. In the case that individuals were shown multiple lineups (as part of a bigger study), it is possible to correct outcome measurements for an individual's visual ability. }
\end{enumerate}

The power of a statistical test is defined as the probability to reject the null hypothesis. Translated to the visual tests, power is the probability to identify the data plot from the lineup. 
Comparing power of competing designs therefore involves comparing percentages of correct responses $p_1$ and $p_2$. An $\alpha\cdot$100\% confidence interval for this comparison is given as 
\[
p_1 - p_2 \pm t_{1-\alpha/2, n-1} \sqrt{p_1(1-p_1)/n_1 + p_2(1-p_2)/n_2},
\]
where $n$ is the Welch-Satterthwaite \cite{welch:1947} estimate of the degrees of freedom. Note that we use $p_i = (x_i+1)/(n_i+1)$ and $n_i+2$ for a better coverage of the confidence interval \cite{agresti:1998}.

>>>>

\begin{quote}
Let $n$ be the number of independent observers and $x_i$ the number of observers who picked plot $i$, $i \in \{1, ..., m\}$, from the lineup. Then $(x_1, x_2, ..., x_m)$ follows a multinomial distribution Mult$_{\pi_1, \pi_2, ..., \pi_m}(x_1, x_2, ..., x_m)$ with $\sum_i \pi_i = 1$, where $\pi_i$ is the probability that plot $i$ is picked by an observer, which we can estimate as $\widehat{\pi}_i = x_i/n$. 
\end{quote}

@@

\section{Comparison of Designs}\label{designs}
We are going to make use of the signal strength gained from multiple viewings of a lineup in order to evaluate competing designs as follows:
\begin{enumerate}
\item{{\bf Create Lineup Data:} create data for a lineup of size $m$ by  creating  $m-1$ permutations of $y$ or, in the case of a simulation study, drawing $m-1$ samples of size $n$ (the number of rows in the data) from the null distribution. Add the original data to the lineup data randomly between 1 and $m$. The {\tt R} package {\tt nullabor} provides a framework for easy creation of lineup data. }
\item{{\bf Create lineups from competing designs:} using the same data, render lineups of all competing designs. }
\item{{\bf Evaluate Lineups:} by presenting the lineups to independent observers. Assess both signal strength and time needed by individuals to come to a decision. Note that each observer should only be exposed to each lineup data once.}
\item{{\bf Evaluate Competing Designs:} differences in signal strength or time to decision are due to differences in the design. In the case that individuals were shown multiple lineups (as part of a bigger study), it is possible to correct outcome measurements for an individual's visual ability. }
\end{enumerate}

%The power of a statistical test is defined as the probability to reject the null hypothesis. Translated to the visual tests, power is the probability to identify the data plot from the lineup. 
Comparing power of competing designs therefore involves comparing percentages of correct responses $\widehat{\pi}_1$ and $\widehat{\pi}_2$. An $\alpha\cdot$100\% confidence interval for this comparison is given as 
\[
\widehat{\pi}_1 - \widehat{\pi}_2 \pm t_{1-\alpha/2, n-1} \sqrt{\widehat{\pi}_1(1-\widehat{\pi}_1)/n_1 + \widehat{\pi}_2(1-\widehat{\pi}_2)/n_2},
\]
where $n$ is the Welch-Satterthwaite \cite{welch:1947} estimate of the degrees of freedom. Note that we use $\widehat{\pi}_i = (x_i+1)/(n_i+1)$ and $n_i+2$ for a better coverage of the confidence interval \cite{agresti:1998}.
